BLAST: Block Applications for Things

### 2022-03-03 demo-eswc22/paper.tex
add text, references and comments

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
%\usepackage{fullpage}
%\usepackage{setspace}
%\onehalfspacing
\usepackage{listings}
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\section{Block-based Visual Programming}
The programming languages currently in use are primarily text-based and are difficult to access for laypersons without prior knowledge.
One possible approach to improve accessibility and simplify the creation of computer programs are so-called Visual Programming Languages (VPL).
VPLs do not require the user to enter any text, they are instead based on graphical elements like blocks, tables or diagrams.
Programs are created by arranging the available graphical elements in the correct order.
The block-based approach of VPLs has become established in recent years, especially as an entry point for novice programmers.

@@

The basic idea of the block-based approach is that predefined blocks with images or text are arranged into programs by using the drag-and-drop principle.
Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
Since blocks can only be arranged in the correct way, no syntax errors can occur \cite{10.11453341221}.
The created block programs can be translated into any predefined programming language, resulting in a normal source code. 
The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
For example, it has been shown that block languages can be successfully used in programming industrial robots \cite{8120406} or executing SPARQL queries \cite{7369012}.
Both areas, which normally require advanced programming skills.

\section{BLAST - Block Applications For Things}
Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{https://developers.google.com/blockly} library.
Blockly is a pure JavaScript library for creating block-based languages and editors.
Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
We have named our block language ''Block Applications For Things'', or BLAST for short (See figure \ref{fig1}).
The browser-based BLAST uses web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.

\begin{figure}
\includegraphics[width=\textwidth]{BL2.PNG}
\caption{Graphical user interface of the BLAST programming environment.} \label{fig1}
\end{figure}

@@

@@

To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction over devices communicating with Bluetooth Low Energy and USB Human Interface Device (HID) Class.
We also provide access to online APIs related to speech input and output.

\begin{center}
\begin{tabular}{ |c|c|c| } 
 \hline
 cell1 & cell2 & cell3 \\ 
 cell4 & cell5 & cell6 \\ 
 cell7 & cell8 & cell9 \\ 
 \hline
\end{tabular}
\end{center}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
%\usepackage{fullpage}
%\usepackage{setspace}
%\onehalfspacing
\usepackage{listings}
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
\usepackage{makecell}
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\section{Block-based Visual Programming}
The programming languages currently in use are primarily text-based and are difficult to access for laypersons without prior knowledge.
One possible approach to improve accessibility and simplify the creation of computer programs is so-called Visual Programming (VP).
% Falls Platz dafür ist, die Definition für VP fand ich besser:
VP as defined by Myers \cite{myers1990taxonomies} refers to any system that allows the user to specify a program in a two (or more) dimensional fashion. Conventional textual languages are not considered two dimensional since the compiler or interpreter processes it as a long, one-dimensional stream. For a more in-depth definition of VP, the reader is referred to \cite{burnett1995visual}. 
VP does not require the user to enter any text, it is instead based on graphical elements like blocks, graphs, tables or diagrams.
Programs are created by arranging the available graphical elements in the correct order.
The block-based approach of VP has become established in recent years, especially as an entry point for novice programmers 
% Vorschläge für Referenzen
\cite{moors2018transitioning} \cite{weintrop2017blocks} \cite{chao2016exploring} \cite{HUNDHAUSEN200722} \cite{10.1145/2787622.2787712}.

@@

The basic idea of the block-based approach is that predefined blocks with images or text are arranged into programs by using the drag-and-drop principle.
Blocks can be geometrically aligned with other compatible blocks, like in a jigsaw puzzle, to form complex programs.
Since blocks can only be arranged in the correct way, no syntax errors can occur \cite{10.11453341221} \cite{maloney2010scratch} \cite{10.1145/1089733.1089734} \cite{lye2014review}.
The created block programs can be translated into any predefined programming language, resulting in a normal source code. 
The block-based approach can be used not only for learning programming concepts, but also for more complex problems.
For example, it has been shown that block languages can be successfully used in programming industrial robots \cite{8120406} \cite{ghazal2016framework} \cite{tomlein2017visual} or executing SPARQL queries \cite{7369012}. Both areas, which normally require advanced programming skills. Furthermore, Ray examined the use of block-based programming languages for IoT devices in \cite{ray2017survey} and concluded that IoT seems to be suitably getting empowered by smooth entanglement and promotion with promising reduction in physical-digital interface. %Das ist ein direktes Zitat, muss man das anders schreiben?

\section{BLAST - Block Applications For Things}
Due to the success of block-based languages in different challenging areas, we have developed our own block language based on Google's Blockly\footnote{https://developers.google.com/blockly/} library. %Momentan zweimal die gleiche Fußnote auf einer Seite.
Blockly is a pure JavaScript library for creating block-based languages and editors.
Our block-based language simplifies the interaction with IoT devices, digital twins or other web resources without the need for a deeper understanding of different programming languages or network protocols such as Bluetooth or HTTP.
We have named our block language ''Block Applications For Things'', or BLAST for short (See figure \ref{fig1}).
The browser-based BLAST uses web Bluetooth to communicate with IoT devices, custom control and command blocks, and generates JavaScript code that can be used by any JavaScript interpreter.
To interact with the IoT devices, BLAST requires custom drivers for each device, which represent an extended form of the WoT TD % Beides noch nicht definiert
 and contain the metadata and interaction affordances as well as the JavaScript code needed for communication.

\begin{figure}
\includegraphics[width=\textwidth]{Blast Screenshot.png}%im Ordner sind noch 2 alternative Screenshots
\caption{Graphical user interface of the BLAST programming environment.} \label{fig1}
\end{figure}

@@

The currently best known tool for programming IoT devices using VP is Node-Red\footnote{https://nodered.org/}. Other than BLAST, Node-Red employs a flow-based programming paradigm, and therefore displays applications as graphs. The nodes in these graphs are black box processes, created by the developers, that can be connected to each other by the end user. The block-based approach utilized by BLAST provides more flexibility as its blocks are a lot more fine grained. Also, Node-Red does not implement the WoT standard, which hinders re-usability of code with applications other than Node-Red. Another application similiar to BLAST is Punya\cite{patton2021punya} an Android App development Application based on the MIT App Inventor\footnote{https://appinventor.mit.edu/}. Like Blast, Punya offers a block-based programming environment able to run SPARQL queries and utilizes services like sending a tweet. But Punya focuses on creating applications for Android devices only and solely communicates with the device's internal hardware. Other than BLAST, Punya apps are capable of working as a LDP-CoAP client to publish and access data on CoAP servers.

@@

To demonstrate how BLAST can interact with WoT devices, we provide a Web of Things abstraction for devices communicating with Bluetooth Low Energy and USB Human Interface Devices (HID).
We also provide access to online APIs related to speech input and output and services like playing audio from a URI or invoking SPARQL queries on an online ressource.

\begin{center}
  \begin{tabular}{|c|c|c|}
  \hline
  Device & Communication & WoT interactions \\
  \hline
  Eddystone Devices & BLE GATT & read/write Eddystone properties \\
  HuskyLens\footnote{https://wiki.dfrobot.com/HUSKYLENS\_V1.0\_SKU\_SEN0305\_SEN0336} & BLE GATT & read sensor properties, invoke forget action \\
  RGB LED Controller\footnote{https://aliexpress.com/item/4000208329326.html} & BLE GATT & write color properties \\
  RuuviTag\footnote{https://ruuvi.com/ruuvitag/} & BLE GATT & \makecell{read sensor properties, read battery property, \\
  read/write txPower property, \\
  read movement counter propert,y \\
  read measurement sequence counter property} \\
  StreamDeck\footnote{https://www.streamdeck.com/} & USB HID & \makecell{write display properties, \\ subscribe to button push events} \\
  Tulogic BlinkStick\footnote{https://www.blinkstick.com/} & USB HID & write color properties \\ 
  Nintendo JoyCon\footnote{https://www.nintendo.com/switch/tech-specs/\#joycon-section} & USB HID \& BLE GATT & \makecell{read sensor properties,\\ subscribe to button push events} \\
  Xiaomi Thermometer\footnote{https://xiaomipedia.com/en/p/xiaomi-electronic-thermometer-and-hygrometer/} & BLE GATT & read sensor properties \\
  \hline
  \end{tabular}

  \begin{tabular}{|c|c|}
  \hline
  Service & WoT interactions \\
  \hline
  Camera & invoke capture image action \\
  Audio & invoke play audio action \\ % TODO
  WebSpeech API & invoke text to speech action, invoke speech to text action \\
  HTTP Requests & invoke send HTTP request action \\
  SPARQL Query & invoke execute SPARQL query action \\
  SOLID & invoke upload to solid container action \\
  \hline
  \end{tabular}
\end{center}
